\documentclass[12pt, a4paper]{article}

\usepackage{hyperref} % allows hyperlinking
\usepackage{xcolor} % For text colors
\definecolor{Maroon}{RGB}{128, 0, 0} % Define maroon color
\definecolor{Gray}{RGB}{120, 120, 120} % Define light gray for footer text
\usepackage{marvosym} % For symbols (phone, email, etc.)
\usepackage{geometry} % For page margins
\geometry{margin=0.75in, top=0.4in} % Adjust top margin to reduce space

% Remove paragraph indentation
\setlength{\parindent}{0pt}

% Hyperlink color settings
\hypersetup{
    colorlinks=true,
    linkcolor=Maroon,
    urlcolor=Maroon
}

% Footer settings
\usepackage{fancyhdr}
\usepackage{courier} % Use Courier New for monospace font
\pagestyle{fancy}
\fancyhf{} % Clear default header/footer
\renewcommand{\headrulewidth}{0pt} % Remove header rule
\renewcommand{\footrulewidth}{0pt} % No footer line

% Define footer text formatting
\fancyfoot[L]{\textcolor{Gray}{\texttt{\textsc{January 2025}}}} % Update manually
\fancyfoot[C]{\textcolor{Gray}{\texttt{\textsc{Brady M. Chisholm-Curriculum Vitae}}}}
\fancyfoot[R]{\textcolor{Gray}{\texttt{\textsc{\thepage}}}}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]

\newcommand{\sectionrule}{%
    \noindent\makebox[\textwidth][l]{\hrulefill}\par\vspace{-0.25em}
}

\begin{document}

% Centered name and contact info
\begin{center}
    {\Large \textsc{Brady M. Chisholm}} \\[0.3em] % Small caps for name
    \normalsize
    \textbf{Email:} \href{mailto:chish071@umn.edu}{chish071@umn.edu} \quad $|$ \quad
    \textbf{Phone:} \href{null}{612-499-6865} \quad $|$ \quad
    \textbf{Website:} \href{http://brady-c.cc}{brady-c.cc} \\
\end{center}

\vspace{0.5em}
\section*{Research Interests}
My research interests focus on understanding how the brain perceives and interacts with the world. 
During my time in Dr. Andrew Oxenham's lab, I engaged in auditory perception research, which introduced 
me to computational neuroscience. My goal is to pursue a Ph.D. that leverages AI, machine learning, and 
computational methods to model biological systems in humans and animals. I aim to contribute to research 
that deciphers how neural activity translates into behavior and decision-making.

\section*{Education}
\textbf{University of Minnesota, Minneapolis, MN} \hfill \textit{Sep 2023--exp. Dec 2025} \\
\textit{Bachelor of Science: Psychology, Minor: Computer Science} \\
University Honors Major \\
- Honors thesis in progress with Dr. Jean-Paul Noel's Neuroscience Lab (expected Dec 2025) \\
- \textbf{Relevant coursework:} Regression and Correlated Data, Calculus I, Biopsychology, Discrete Structures (I.P.)\\
\\
\textbf{Gustavus Adolphus College, St. Peter, MN} \hfill \textit{Sep 2022--May 2023} \\
- Participated in two semesters of research apprenticeship \\
- Awarded two semesters of research grant funding \\
- Men’s Varsity Swim \& Dive Competitor \\
- \textbf{Relevant coursework:} Attention (seminar), Latin I \& II, Statistics 101

\section*{Experience}
\textbf{Research Assistant, UMN Neuroscience Department} \hfill \textit{Jan 2025--Present} \\
Dr. Jean-Paul Noel's Cognitive and Systems Neuroscience Laboratory \\
- Decoding neural activity and decision-making in mice

\textbf{Research Assistant, UMN Psychology Department} \hfill \textit{Dec 2023--Present} \\
Dr. Andrew Oxenham's Auditory Perception and Cognition Laboratory \\
- Data collection: EEG, audiograms \\
- Statistical analysis: GAM, GCA, ICA, linear regression, ANOVA \\
- Various independent projects  

\textbf{Research Assistant, UMN Ecology, Evolution, and Behavior} \hfill \textit{Jun 2024--Aug 2024} \\
Dr. Mark Bee's Animal Communication Laboratory \\
- Seasonal assistant for \textit{Hyla chrysoscelis} and \textit{Hyla versicolor} research \\
- Animal handling, strict experiment protocols, exploratory statistical analysis \\
- Assisted in craniotomies and brain sample extraction

\section*{Grants and Awards}
\textbf{Career Grant Monies Awarded:} \$5,000

\textbf{Undergraduate Research Opportunities Project Grant} \hfill \textit{May 2024} \\
- \$2,100 research grant for \textit{Analysis of Pupillometry Data} with Juraj Mesik

\textbf{Dean’s First-Year Research and Academics Scholarship} \hfill \textit{Jan 2024} \\
- \$900 scholarship for research with Dr. Oxenham \\
- Assisted in EEG and pupillometry data analysis

\textbf{Presidential Research Grant, Gustavus Adolphus College} \hfill \textit{May 2023} \\
- \$1,500 summer research grant

\section*{Publications and Presentations}
\textbf{Publications} \\
1. Brady M. Chisholm, Juraj Mesik. \textit{An Analysis of Pupillometry Data in a Speech Paradigm}. Nov 2024.

\textbf{Posters and Presentations} \\
2. Registered poster presenter for ASA 2025: \textit{Analysis of Pupillometric Fatigue in Listening Effort} \\
3. Brady M. Chisholm, Lauren Hecht, \textit{Entomophobic Responses and the Rubber Hand Illusion}, Spring Research Day, Gustavus Adolphus College, May 2023

\section*{Professional Membership and Service}
\textbf{Journal Reviewer} \hfill \textit{Minnesota Undergraduate Research \& Academic Journal (2025)} \\
\textbf{Psi Chi International Honor Society} \hfill \textit{Winner, R Data Science Competition (Oct 2024)} \\
\textbf{Gustavus Adolphus College} \hfill \textit{Presidents Honor Research Award (May 2023)} \\
\textbf{Eagle Scout, Boy Scouts of America} \hfill \textit{Nov 2021}

\section*{Projects}
\textbf{A GAM Analysis of Pupillometry Data} \hfill \textit{2024} \\
- Fatigue effects in pupillometry data modeled using GAM

\textbf{The CodeR Sessions} \hfill \textit{2024--Present} \\
- Increasing accessibility for R and data science education \\
- Project website: \href{http://brady-c.cc}{brady-c.cc}

\section*{Research Skills and Technologies}
\textbf{Research Skills:} EEG data collection, CAD, animal handling, audiograms, chemical handling \\
\textbf{Technology:} MATLAB, Python, R, HTML, Git, GitHub

\end{document}
