\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=0.8in}
\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, partopsep=0pt}  % Compact spacing for bullet points
\pagenumbering{gobble}
\usepackage{titlesec}
\usepackage{parskip}

% Formatting section titles
\titlespacing*{\section}{0pt}{1em}{0.5em}
\titleformat{\section}{\bfseries\large}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    \textbf{\Large Brady M. Chisholm} \\
    Minneapolis, MN \\
    E: chish071@umn.edu \quad — \quad C: 612.499.6865 \quad — \quad Website: brady-c.cc
\end{center}

\vspace{-0.1in}  % Slightly reduced space between header and first section

\section*{Education}
\vspace{-0.02in}

\textbf{University of Minnesota, Twin Cities} \hfill Minneapolis, MN \\
College of Liberal Arts \hfill September 2023-Present \\
B.S. Psychological Science \\
Minor in Computer Science \\
University Honors Program Major
\begin{itemize}
    \item Research Assistant, Auditory Perception and Cognition Laboratory under Dr. Andrew Oxenham
    \item PsyChi Club Member
\end{itemize}

\textbf{Gustavus Adolphus College} \hfill St. Peter, MN \\
B.S. in Psychology \hfill August 2022-May 2023
\begin{itemize}
    \item Presidential Research Grant Recipient, Summer 2023
    \item Swanson Holcomb Undergraduate Research Experience Grant Recipient, Spring 2023
    \item Research Apprentice, Fall 2022-Spring 2023
    \item Varsity Swim and Dive Competitor, 2022-2023
\end{itemize}

\section*{Work Experience}
\vspace{-0.05in}

\textbf{Supportive Living Solutions} \hfill Minneapolis, MN \\
Mental Health Advocate II \hfill June 2023-Present
\begin{itemize}
    \item Client caseload management, medication administration 
    \item On-The-Job Trainer for new company staff 
\end{itemize}

\textbf{South Suburban Athletic Conference} \hfill Metro Area, MN \\
Head Official \hfill September 2018-Present
\begin{itemize}
    \item Referee for youth sports and tournaments.
    \item Managed teams of officials and trained new referees.
\end{itemize}

\textbf{The Gustavian Weekly} \hfill St. Peter, MN \\
Lead Copy Editor \hfill August 2022-June 2023
\begin{itemize}
    \item Managed a team of editors and oversaw final publication review.
\end{itemize}

\textbf{Kwik Trip Inc.} \hfill Lakeville, MN \\
Guest Service Coworker \hfill June 2019-May 2023
\begin{itemize}
    \item Handled customer service, inventory, and store operations.
\end{itemize}

\vspace{0.1in}

\section*{Awards and Achievements}
\vspace{-0.05in}

\begin{itemize}
    \item Residential Directors Service Award, February 2024
    \item Deans First-Year Research and Creative Scholar Grant Recipient, Spring 2024
    \item Presidential Research Grant Recipient, Summer 2023
    \item Swanson Holcomb Research Grant Recipient, Spring 2023
    \item President’s Academic Honor List, Fall 2022, Spring 2023
    \item Eagle Scout, November 2021
    \item Varsity Captain, Apple Valley Swim and Dive, 2020-2022
\end{itemize}

\end{document}
